---
title: "FScanR: detect programmed ribosomal frameshifting events from various genomes"
author: "Xiao Chen\\

        Columbia University Medical Center"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    toc: false
    theme: cayman
    highlight: github
  pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{ggtree}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r style, echo=FALSE, results="asis", message=FALSE}
knitr::opts_chunk$set(tidy = FALSE,
		   message = FALSE)
```


```{r echo=FALSE}
CRANpkg <- function (pkg) {
    cran <- "https://CRAN.R-project.org/package"
    fmt <- "[%s](%s=%s)"
    sprintf(fmt, pkg, cran, pkg)
}

Biocpkg <- function (pkg) {
    sprintf("[%s](http://bioconductor.org/packages/%s)", pkg, pkg)
}

```


'FScanR' identifies Programmed Ribosomal Frameshifting (PRF) events from BLASTX output 
in tab format containing the best hits of targeted mRNA/cDNA sequences against 
the peptide library of the same species or a close relative.

To acquire the input file with 14 columns in tab-delimited format, which is generated by BLASTX, parameters should be used for BLASTX: 

	-outfmt '6 qseqid sseqid pident length mismatch gapopen qstart qend sstart send evalue bitscore qframe sframe'

For details, please visit <https://doi.org/10.1111/1755-0998.13023>.

##  Install FScanR in R (>= 3.5.0)

	library(devtools)
	install_github("seanchen607/FScanR")
	library(FScanR)

##  What is Programmed Ribosomal Frameshifting (PRF)?

Ribosomal frameshifting, also known as translational frameshifting or translational recoding, is a biological phenomenon 
that occurs during translation that results in the production of multiple, unique proteins from a single mRNA. 
The process can be programmed by the nucleotide sequence of the mRNA and is sometimes affected by the secondary, 3-dimensional mRNA structure.
It has been described mainly in viruses (especially retroviruses), retrotransposons and bacterial insertion elements, and also in some cellular genes.

For details, please visit [Ribosomal frameshift](https://en.wikipedia.org/wiki/Ribosomal_frameshift).

##  Citation

If you use [FScanR](https://github.com/seanchen607/FScanR) in
published research, please cite the most appropriate paper(s) from this
list:

1.  **X Chen**, Y Jiang, F Gao<sup>\*</sup>, W Zheng, TJ Krock, NA Stover, C Lu, LA Katz & W Song (2019). 
    Genome analyses of the new model protist Euplotes vannus focusing on genome rearrangement and resistance 
    to environmental stressors. ***Molecular Ecology Resources***, 19(5):1292-1308. doi:
    [10.1111/1755-0998.13023](https://doi.org/10.1111/1755-0998.13023).

